make STEAM clear

### 2019-12-04 mstemc/mstemc.tex
modify 20191202

\section{Videos}
\label{sec:orgd3ae832}

\section{Posts}
\label{sec:org7648261}

\section{Projects}
\label{sec:orgec1d3eb}

\subsection{my workflow of creating a video}
\label{sec:org3bbb651}
During the creation of one video, several tools are tuned to fit my workflow. In
this project several videos and posts will be created to make my workflow clear.

@@

\subsubsection{Emacs}
\label{sec:org42d9799}

@@

\begin{enumerate}
\item program and debug
\label{sec:orgb2fe87f}

@@

\item Org mode - journalize your work
\label{sec:orgeea2f15}

@@

\item Org mode - get things done
\label{sec:orgc04d679}

\item Org mode - write a diary
\label{sec:orgfef1783}

\item Org mode - export your Org file
\label{sec:org4bcf25c}

\item program and debug
\label{sec:org1802ebb}

\item writing latex
\label{sec:orgbcbd545}
\item org-journal
\label{sec:orgef55573}

@@

\item ox-hugo
\label{sec:org5381774}

@@

\item preview tikz picture in Org
\label{sec:org9189e37}

A minimum working example is shown as below
\end{enumerate}

\subsubsection{Hugo}
\label{sec:org02f26a1}

@@

\subsubsection{manim}
\label{sec:orge522a09}

\subsubsection{blender}
\label{sec:orgcd33ab5}

\section{Courses}
\label{sec:orgcd12774}
\end{document}

>>>>

\section{Videos}
\label{sec:orgfaf9643}

\section{Posts}
\label{sec:org8bd76bc}

\section{Projects}
\label{sec:org9f3dc59}

\subsection{my workflow of creating a video}
\label{sec:org0f22a5a}
During the creation of one video, several tools are tuned to fit my workflow. In
this project several videos and posts will be created to make my workflow clear.

@@

\subsubsection{Emacs}
\label{sec:orge0a91d3}

@@

\begin{enumerate}
\item program and debug
\label{sec:orgb4f0839}

@@

\item Org mode - journalize your work
\label{sec:org106db98}

@@

\item Org mode - get things done
\label{sec:org39b4c74}

\item Org mode - write a diary
\label{sec:org82f34e2}

\item Org mode - export your Org file
\label{sec:org060ee3f}

\item program and debug
\label{sec:orgb408704}

\item writing latex
\label{sec:org821d574}
\item org-journal
\label{sec:org17da77b}

@@

\item ox-hugo
\label{sec:orgc0903f5}

@@

\item preview tikz picture in Org
\label{sec:org0703751}

A minimum working example is shown as below
\begin{center}
\includegraphics[width=.9\linewidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png}
\end{center}
\end{enumerate}

\subsubsection{Hugo}
\label{sec:org79ed269}

@@

\subsubsection{manim}
\label{sec:org6ba75eb}

\subsubsection{blender}
\label{sec:org546be21}

\section{Courses}
\label{sec:orgf7e6e3a}
\end{document}
